Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-07 prop_letter.tex
intro but need to fix sentence about classical

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ 
quantifying the effect of finite-precision uncertainties on measurement 
outcomes, reducing to the purely deterministic
Kochen-Specker case for $\delta=0$, can resolve the question of effect
of finite precision and imperfections on contextuality.  A remarkable
consequence of our analysis is that not only does the
quantum-mechanical requirement for contextuality continue to hold,
thus maintaining the Kochen-Specker result for a \emph{non-vanishing}
range of $\delta$, but that at a \emph{certain fixed value} of
$\delta$, there is a sharp transition, parallel in its consequences
to, say, a phase transition, to \emph{non-contextuality}; that is,
quantum mechanics suddenly fails to hold, and all variables can be
specified simultaneously, turning the theory effectively into a
classical theory that can be specified consistently by hidden
variables.  
\yutsung{The part after ``that is'' looks strange.
\begin{enumerate}
\item The Kochen-Specker theorem is not about quantum mechanics, is about whether
quantum mechanics can be simulated by a non-contextual deterministic hidden
variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
doesn't make a lot sense.
\item The question is whether there exist a QIVPM means ``a classical theory
consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
I need to check whether it qualities as a classical probabilistic hidden variable
theory\ldots(?)
\end{enumerate}
}
These results provide a new insight into the
Meyer-Mermin debate by presenting a theory in which there is a
\emph{parameter} interpolating between what appeared previously to be
irreconcilable interpretations of contextuality.

>>>>

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
effect of finite-precision uncertainties on measurement outcomes,
reducing to the purely deterministic Kochen-Specker case for
$\delta=0$, can resolve the question of the effect of finite precision
and imperfections on contextuality.  A remarkable consequence of our
analysis is that not only does the quantum-mechanical requirement for
contextuality continue to hold, thus maintaining the Kochen-Specker
result for a \emph{non-vanishing} range of $\delta$, but that at a
\emph{certain fixed value} of $\delta$, there is a sharp transition,
parallel in its consequences to, say, a phase transition, to
\emph{non-contextuality}; that is, suddenly a quantum system can be
simulated by a non-contextual hidden variable theory, turning the
system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable interpretations
of contextuality.
